---
title: "Meta-Analyses"
author: "Rohit Daniel"
output: html_document
---

```{r setup, results='hide', echo=FALSE}
Sys.setlocale("LC_ALL", "Norwegian_Norway.65001")  # UTF-8
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
knitr::opts_knit$set(
  root.dir = "C:/Users/rodan/OneDrive - Høgskulen på Vestlandet/Dokumenter/GitHub/PhD_Analyses/RQ1/Fisher_Z_CSV"
  )
```


# 0. Load required R packages
```{r}
# Load required package
library(tidyverse)
library(metafor)
library(tikzDevice)
```

# 1. Import and prepare effect sizes for meta analysis
```{r}
# Import Fisher z from correlational and experimental studies
corr_fisher_z <- read.csv("corr_fisher_z_cleaned.csv", header = TRUE, fileEncoding = 'UTF-8')
exp_fisher_z <- read.csv("exp_fisher_z_cleaned.csv", header = TRUE, fileEncoding = 'UTF-8')

# Combine correlational and experimental Fisher z tibbles
combined_effects <- 
  corr_fisher_z %>% 
  bind_rows(exp_fisher_z)
```

# 2. Meta-analysis of associations between feedback effects and self-efficacy
```{r}
# Filter associations between feedback and self-efficacy
fb_se <- 
  combined_effects |> 
  filter((grepl("Feedback", Variable_A, ignore.case = TRUE) & grepl("Self[- ]?Efficacy", Variable_B, ignore.case = TRUE)) |
           (grepl("Feedback", Variable_B, ignore.case = TRUE) & grepl("Self[- ]?Efficacy", Variable_A, ignore.case = TRUE))) |> 
  mutate(
    across(contains("Type"), as.factor),
    Setting = as.factor(Setting), 
    Design = as.factor(Design)
    )

# Create unique effect size identifier for multilevel modeling
fb_se <- fb_se |> mutate(Effect_ID = row_number())

# Specify null model
res_fb_se_null <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  data = fb_se,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

# Specify random-effects multi-level meta-regression models
res_fb_se_model_1 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Setting,               # Setting as moderator (factor auto-dummy coded)
  data = fb_se,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

res_fb_se_model_2 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Study_Type,               # Setting as moderator (factor auto-dummy coded)
  data = fb_se,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

res_fb_se_model_3 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Setting + Study_Type,               # Setting as moderator (factor auto-dummy coded)
  data = fb_se,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

res_fb_se_model_4 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Setting * Study_Type,               # Setting as moderator (factor auto-dummy coded)
  data = fb_se,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)
```

## Inspect models
```{r}
# Likelihood ratio tests
comp1_fb_se <- anova(res_fb_se_null, res_fb_se_model_1, refit=TRUE)
comp2_fb_se <- anova(res_fb_se_null, res_fb_se_model_2, refit=TRUE)
comp3_fb_se <- anova(res_fb_se_null, res_fb_se_model_3, refit=TRUE)
comp4_fb_se <- anova(res_fb_se_null, res_fb_se_model_4, refit=TRUE)

print("=== MODEL1 COMPARISON SUMMARY ===")
print(comp1_fb_se)

print("=== MODEL2 COMPARISON SUMMARY ===")
print(comp2_fb_se)

print("=== MODEL3 COMPARISON SUMMARY ===")
print(comp3_fb_se)

print("=== MODEL4 COMPARISON SUMMARY ===")
print(comp4_fb_se)
```
In the meta-regression for feedback-self-efficacy associations, I compared a null model (no moderators) against four alternatives: Model 1 (~ Setting), Model 2 (~ Study_Type), Model 3 (~ Study_Type + Setting), and Model 4 (~ Study_Type * Setting). Selection prioritized AIC, BIC, AICc, likelihood ratio tests (LRT), and residual heterogeneity (QE).

Model 1 was selected as the best fit due to its lowest AIC (50.33), BIC (57.16), and AICc (52.93), highly significant LRT improvement over the null (p = 0.0026), and substantial QE reduction (from 836 to 415). It balanced explanatory power and parsimony better than the others, which showed higher criteria or unnecessary complexity. The overlap between Setting and Study_Type (experimental studies mostly in individual settings; correlational in classroom/small group) likely caused redundancy in combined models, favoring Setting alone for clearer, more efficient moderation.

```{r}
# Calculate pseudo R^2
R2_fb_se <- round(((res_fb_se_null$sigma2[1] - res_fb_se_model_1$sigma2[1]) / res_fb_se_null$sigma2[1]) * 100, 1)
print(paste("Feedback setting explains", R2_fb_se, "% of study-level variance"))

# Test residual heterogeneity
print("Residual heterogeneity test:", quote=FALSE)
print(res_fb_se_model_1$QE)

# Model summaries
print("FULL MODEL:", quote=FALSE); summary(res_fb_se_model_1)
print("NULL MODEL:", quote=FALSE); summary(res_fb_se_null)

# Detailed coefficients (with p-values)
coef_tab_fb_se <- coef(summary(res_fb_se_model_1))
print(coef_tab_fb_se)
```

```{r}
# Overall (null) pooled effect prediction
p_overall_fb_se <- predict(res_fb_se_null)

# Predicted means by Setting levels
levels_setting <- levels(fb_se$Setting)

pred_by_setting_fb_se <- lapply(levels_setting, function(s) {
  # Create design matrix for the specific level
  Xnew <- model.matrix(~ Setting, data = data.frame(Setting = factor(s, levels = levels_setting)))
  pr <- predict(res_fb_se_model_1, newmods = Xnew[, -1, drop = FALSE])
  data.frame(
    Effect = s,
    Fisher_z = pr$pred,
    CI_lb = pr$ci.lb,
    CI_ub = pr$ci.ub,
    p_value = 2 * (1 - pnorm(abs(pr$pred / pr$se)))  # Two-tailed test: mean != 0
  )
}) |> bind_rows()

# Combine into final table
results_fb_se <- bind_rows(
  data.frame(
    Effect = "Overall",
    Fisher_z = p_overall_fb_se$pred,
    CI_lb = p_overall_fb_se$ci.lb,
    CI_ub = p_overall_fb_se$ci.ub,
    p_value = 2 * (1 - pnorm(abs(p_overall_fb_se$pred / p_overall_fb_se$se)))
  ),
  pred_by_setting_fb_se
)

# Back-transform for interpretation (Fisher z to r)
results_fb_se$Correlation_r <- tanh(results_fb_se$Fisher_z)
results_fb_se$CI_r_lb <- tanh(results_fb_se$CI_lb)
results_fb_se$CI_r_ub <- tanh(results_fb_se$CI_ub)

# Optional: p-value for Adaptive vs Maladaptive (difference test)
p_diff_individual_vs_classroom <- coef_tab_fb_se["SettingIndividual", "pval"]
p_diff_small_groups_vs_classroom <- coef_tab_fb_se["SettingSmall_Groups", "pval"]

# Format p-values for publication (show <0.001 if applicable)
results_fb_se$p_value_formatted <- ifelse(results_fb_se$p_value < 0.001, "<0.001", sprintf("%.3f", results_fb_se$p_value))

# Round numeric columns (except formatted p-value)
num_cols <- sapply(results_fb_se, is.numeric) & colnames(results_fb_se) != "p_value_formatted"
results_fb_se[num_cols] <- lapply(results_fb_se[num_cols], function(x) round(x, 3))

# Print results table (using r-scale CIs for consistency)
print("=== META-REGRESSION RESULTS ===")
print(results_fb_se[, c("Effect", "Fisher_z", "Correlation_r", "CI_r_lb", "CI_r_ub", "p_value_formatted")])

# Publication summary
cat("\n=== PUBLICATION SUMMARY ===\n")
for (i in 1:nrow(results_fb_se)) {
  cat(sprintf("%12s: r = %6.3f [%.3f, %.3f], p = %s\n",
              results_fb_se$Effect[i],
              results_fb_se$Correlation_r[i],
              results_fb_se$CI_r_lb[i],
              results_fb_se$CI_r_ub[i],
              results_fb_se$p_value_formatted[i]))
}

# Individual vs. Classroom difference test p-value
cat("\nIndividual vs Classroom difference test p-value: ",
    ifelse(p_diff_individual_vs_classroom < 0.001, "<0.001", sprintf("%.3f", p_diff_individual_vs_classroom)),
    "\n", sep="")

# Small Groups vs. Classroom difference test p-value
cat("\nIndividual vs Classroom difference test p-value: ",
    ifelse(p_diff_small_groups_vs_classroom < 0.001, "<0.001", sprintf("%.3f", p_diff_small_groups_vs_classroom)),
    "\n", sep="")

# saveRDS(results, "meta_regression_results.rds")
# write.csv(results, "meta_regression_results.csv")
```

```{r}
# Forest plot
forest(res_fb_se_model_1, 
       slab = paste0(fb_se$Study, " (", fb_se$Setting, ")"),
       xlab = expression("Fisher's" ~ italic(z)),
       refline = 0,
       digits = c(2, 0),
       header = c("Study (Feedback Setting)", "Fisher z [95% CI]"),
       addfit = TRUE
)
```

# 3. Meta-analyss of associations between feedback and attributions

```{r}
# Filter associations between feedback and attributions
fb_attr <- 
  combined_effects |> 
  filter((grepl("Feedback", Variable_A, ignore.case = TRUE) & grepl("Attributions", Variable_B, ignore.case = TRUE)) |
           (grepl("Feedback", Variable_B, ignore.case = TRUE) & grepl("Attributions", Variable_A, ignore.case = TRUE))) |> 
  mutate(
    across(contains("Type"), as.factor),
    Setting = as.factor(Setting), 
    Design = as.factor(Design)
    )

# Create unique effect size identifier for multilevel modeling
fb_attr <- fb_attr |> mutate(Effect_ID = row_number())

# Specify null model
res_fb_attr_null <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  data = fb_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

# Specify random-effects multi-level meta-regression models
res_fb_attr_model_1 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Attribution_Type,      # Setting as moderator (factor auto-dummy coded)
  data = fb_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

res_fb_attr_model_2 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Setting,               # Setting as moderator (factor auto-dummy coded)
  data = fb_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

res_fb_attr_model_3 <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Attribution_Type + Setting,               # Setting as moderator (factor auto-dummy coded)
  data = fb_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)
```

## Inspect models
```{r}
# Likelihood ratio tests
comp1_fb_attr <- anova(res_fb_attr_null, res_fb_attr_model_1, refit=TRUE)
comp2_fb_attr <- anova(res_fb_attr_null, res_fb_attr_model_2, refit=TRUE)
comp3_fb_attr <- anova(res_fb_attr_null, res_fb_attr_model_3, refit=TRUE)

print("=== MODEL1 COMPARISON SUMMARY ===")
print(comp1_fb_attr)

print("=== MODEL2 COMPARISON SUMMARY ===")
print(comp2_fb_attr)

print("=== MODEL3 COMPARISON SUMMARY ===")
print(comp3_fb_attr)
```
In the meta-regression for feedback-attribution associations, I compared a null model (no moderators) against three alternatives: Model 1 (~ Attribution_Type), Model 2 (~ Setting), and Model 3 (~ Attribution_Type + Setting). Selection prioritized AIC, BIC, AICc, likelihood ratio tests (LRT), and residual heterogeneity (QE).

Model 1 was selected as the best fit due to its lowest AIC (78.79), BIC (85.54), and AICc (79.93), highly significant LRT improvement over the null (p = 0.0077), and substantial QE reduction (from 206.85 to 179.68). It balanced explanatory power and parsimony better than the others, which showed higher criteria or unnecessary complexity. The overlap between Attribution_Type and Setting (e.g., potential clustering by study or design) likely caused redundancy in the combined model, favoring Attribution_Type alone for clearer, more efficient moderation.


```{r}
# Calculate pseudo R^2
R2_fb_attr <- round(((res_fb_attr_null$sigma2[1] - res_fb_attr_model_1$sigma2[1]) / res_fb_attr_null$sigma2[1]) * 100, 1)
print(paste("Attribution type explains", R2_fb_attr, "% of study-level variance"))

# Test residual heterogeneity
print("Residual heterogeneity test:", quote=FALSE)
print(res_fb_attr_model_1$QE)

# Model summaries
print("FULL MODEL:", quote=FALSE); summary(res_fb_attr_model_1)
print("NULL MODEL:", quote=FALSE); summary(res_fb_attr_null)

# Detailed coefficients (with p-values)
coef_table_fb_attr <- coef(summary(res_fb_attr_model_1))
print(coef_table_fb_attr)
```


```{r}
# Overall effect from null model
p_overall_fb_attr <- predict(res_fb_attr_null)

# Predicted means for each Attribution_Type level (correct CIs via vcov)
levels_attribution_type <- levels(fb_attr$Attribution_Type)

pred_levels <- lapply(levels_attribution_type, function(lv) {
  Xnew <- model.matrix(~ Attribution_Type,
                       data = data.frame(Attribution_Type = factor(lv, levels = levels_attribution_type)))
  pr <- predict(res_fb_attr_model_1, newmods = Xnew[, -1, drop = FALSE])  # moderator cols only

  data.frame(
    Effect   = lv,
    Fisher_z = pr$pred,
    SE       = pr$se,
    CI_lb    = pr$ci.lb,
    CI_ub    = pr$ci.ub,
    p_value  = 2 * (1 - pnorm(abs(pr$pred / pr$se)))  # test mean != 0
  )
}) |> do.call(rbind, args = _)

# Combine with "Overall" (null model)
results_fb_attr <- rbind(
  data.frame(
    Effect   = "Overall",
    Fisher_z = p_overall_fb_attr$pred,
    SE       = p_overall_fb_attr$se,
    CI_lb    = p_overall_fb_attr$ci.lb,
    CI_ub    = p_overall_fb_attr$ci.ub,
    p_value  = 2 * (1 - pnorm(abs(p_overall_fb_attr$pred / p_overall_fb_attr$se)))
  ),
  pred_levels
)

# Back-transform to r for interpretation
results_fb_attr$Correlation_r <- tanh(results_fb_attr$Fisher_z)
results_fb_attr$CI_r_lb       <- tanh(results_fb_attr$CI_lb)
results_fb_attr$CI_r_ub       <- tanh(results_fb_attr$CI_ub)

# Optional: p-value for Adaptive vs Maladaptive (difference test)
p_diff_maladaptive_vs_adaptive <- coef_table_fb_attr["Attribution_TypeMaladaptive", "pval"]

# Round numeric columns
num_cols <- c("Fisher_z","SE","CI_lb","CI_ub","p_value","Correlation_r","CI_r_lb","CI_r_ub")
results_fb_attr[num_cols] <- lapply(results_fb_attr[num_cols], \(x) round(x, 3))

# Format p-values
results_fb_attr$p_value_formatted <- ifelse(results_fb_attr$p_value < 0.001, "<0.001",
                                            sprintf("%.3f", results_fb_attr$p_value))

# DISPLAY FINAL PUBLICATION TABLE
cat("\n=== ATTRIBUTION TYPE META-REGRESSION RESULTS ===\n")
print(results_fb_attr[, c("Effect","Fisher_z","Correlation_r","CI_lb","CI_ub","p_value_formatted")])

# PUBLICATION SUMMARY
cat("\n=== PUBLICATION SUMMARY ===\n")
for (i in 1:nrow(results_fb_attr)) {
  cat(sprintf("%15s: r = %6.3f [%.3f, %.3f], p = %s\n",
              results_fb_attr$Effect[i],
              results_fb_attr$Correlation_r[i],
              results_fb_attr$CI_r_lb[i],
              results_fb_attr$CI_r_ub[i],
              results_fb_attr$p_value_formatted[i]))
}

# Adaptive vs. Maladaptive difference test p-value
cat("\nMaladaptive vs Adaptive difference test p-value: ",
    ifelse(p_diff_maladaptive_vs_adaptive < 0.001, "<0.001", sprintf("%.3f", p_diff_maladaptive_vs_adaptive)),
    "\n", sep="")

# saveRDS(results, "meta_regression_results.rds")
# write.csv(results, "meta_regression_results.csv")
```

```{r}
# Forest plot
forest(res_fb_attr_model_1, 
       slab = paste0(fb_attr$Study, " (", fb_attr$Attributions, ")"),
       xlab = expression("Fisher's" ~ italic(z)),
       refline = 0,
       header = c("Study (Attribution Type)", "Fisher z [95% CI]"))
```

# 4. Meta-analysis of associations between self-efficacy and attributions
```{r}
# Filter associations between self-efficacy and attributions
se_attr <- 
  combined_effects |> 
  filter((grepl("Self[- ]?Efficacy", Variable_A, ignore.case = TRUE) & grepl("Attributions", Variable_B, ignore.case = TRUE)) |
           (grepl("Self[- ]?Efficacy", Variable_B, ignore.case = TRUE) & grepl("Attributions", Variable_A, ignore.case = TRUE))) |> 
  mutate(
    across(contains("Type"), as.factor),
    Setting = as.factor(Setting), 
    Design = as.factor(Design)
    )

# Create unique effect size identifier for multilevel modeling
se_attr <- se_attr |> mutate(Effect_ID = row_number())

# Specify null model
res_se_attr_null <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  data = se_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)

# Specify random-effects multi-level meta-regression models
res_se_attr <- rma.mv(
  yi = Fisher_z,                  # Outcome: Fisher-transformed correlations
  V = VI_z,                       # Sampling variances: 1/(n-3) per effect
  random = list(~ 1 | Study,      # Random intercept for Study
                ~ 1 | Effect_ID), # Random intercept for Effect_ID
  mods = ~ Study_Type,      # Setting as moderator (factor auto-dummy coded)
  data = se_attr,
  method = "REML",                # Restricted maximum likelihood
  control = list(optimizer="optim")
)
```

```{r}
# Likelihood ratio test
model_comparison_se_attr <- anova(res_se_attr_null, res_se_attr, refit=TRUE)
print(model_comparison_se_attr)
```
In the meta-regression for self-efficacy-attribution associations, I compared a null model (no moderators) against a moderated model (~ Attribution_Type). Selection prioritized AIC, BIC, AICc, likelihood ratio tests (LRT), and residual heterogeneity (QE), along with pseudo R² for variance explained.

The null model was selected as the best fit due to its lower AIC (18.12), BIC (18.36), and AICc (24.12), with a non-significant LRT (p = 0.6896) indicating no improvement from moderation. The pseudo R² was negative (-336.9%), suggesting the moderator explained no variance and potentially worsened fit. The moderated model showed minimal QE reduction (from 483.61 to 477.42) but added unnecessary complexity, favoring the parsimonious null model for this dataset.

## Inspect models
```{r}
# Test residual heterogeneity
print("Residual heterogeneity test:", quote=FALSE)
print(res_se_attr_null$QE)

# Model summaries
print("NULL MODEL:", quote=FALSE); summary(res_se_attr_null)

# Detailed coefficients (with p-values)
coef_table_se_attr <- coef(summary(res_se_attr_null))
print(coef_table_se_attr)
```


```{r}
# Overall effect from null model
p_overall_se_attr <- predict(res_se_attr_null)

# FIXED PREDICTIONS - Direct coefficient extraction
results_se_attr <- data.frame(
  Effect = c("Overall", "Maladaptive", "Adaptive"),
  Fisher_z = c(
    p_overall_se_attr$pred,                                          # Overall pooled effect
    coef_table_se_attr["intrcpt", "estimate"],                       # Maladaptive = intercept
    coef_table_se_attr["intrcpt", "estimate"] + coef_table_se_attr["Attribution_TypeAdaptive", "estimate"]  # Adaptive
  ),
  p_value = c(
    2 * (1 - pnorm(abs(p_overall_se_attr$pred / p_overall_se_attr$se))),     # Overall vs 0
    coef_table_se_attr["intrcpt", "pval"],                           # Maladaptive vs 0
    coef_table_se_attr["Attribution_TypeAdaptive", "pval"]           # Adaptive vs Maladaptive
  )
)

# Add CIs (direct from model)
results_se_attr$CI_lb <- c(
  p_overall_se_attr$ci.lb,
  coef_table_se_attr["intrcpt", "ci.lb"],
  coef_table_se_attr["intrcpt", "ci.lb"] + coef_table_se_attr["Attribution_TypeAdaptive", "ci.lb"]
)
results_se_attr$CI_ub <- c(
  p_overall_se_attr$ci.ub,
  coef_table_se_attr["intrcpt", "ci.ub"],
  coef_table_se_attr["intrcpt", "ci.ub"] + coef_table_se_attr["Attribution_TypeAdaptive", "ci.ub"]
)

# Back-transform to correlations
results_se_attr$Correlation_r <- round(tanh(results_se_attr$Fisher_z), 3)
results_se_attr$CI_r_lb <- round(tanh(results_se_attr$CI_lb), 3)
results_se_attr$CI_r_ub <- round(tanh(results_se_attr$CI_ub), 3)

# Round numeric columns
results_se_attr[, c("Fisher_z", "CI_lb", "CI_ub", "p_value")] <- 
  lapply(results_se_attr[, c("Fisher_z", "CI_lb", "CI_ub", "p_value")], round, 3)

# Format p-values
results_se_attr$p_value_formatted <- ifelse(results_se_attr$p_value < 0.001, "<0.001", 
                                          sprintf("%.3f", results_se_attr$p_value))

# DISPLAY FINAL PUBLICATION TABLE
cat("\n=== ATTRIBUTION TYPE META-REGRESSION RESULTS ===\n")
print(results_se_attr[, c("Effect", "Fisher_z", "Correlation_r", "CI_lb", "CI_ub", "p_value_formatted")])

# PUBLICATION SUMMARY
cat("\n=== PUBLICATION SUMMARY ===\n")
for (i in 1:nrow(results_se_attr)) {
  cat(sprintf("%15s: r = %6.3f [%.3f, %.3f], p = %s\n",
              results_se_attr$Effect[i],
              results_se_attr$Correlation_r[i],
              results_se_attr$CI_r_lb[i],
              results_se_attr$CI_r_ub[i],
              results_se_attr$p_value_formatted[i]))
}

# saveRDS(results, "meta_regression_results.rds")
# write.csv(results, "meta_regression_results.csv")
```

```{r}
# Forest plot
forest(res_se_attr, 
       slab = paste0(se_attr$Study, " (", se_attr$Attributions, ")"),
       xlab = expression("Fisher's" ~ italic(z)),
       refline = 0,
       header = c("Study (Attribution Type)", "Fisher z [95% CI]"))
```